---
title: "MC Template Title"
author: "Your Name"
affiliation: "Montgomery College"
date: last-modified
title-block-banner: "#51237F"
toc: true
number-sections: true
format: 
  html:
    fig-width: 8
    fig-height: 6
    page-layout: full
    embed-resources: true
editor: visual
editor_options: 
  chunk_output_type: console
execute:
  echo: false
  warning: false
  message: false
  keep-md: true
---

```{r}
#| label: libraries

require(tidyverse)
require(gt)
require(mcirp)
```

```{r}
#| label: pull_data
#| cache: true

source("DataPull.R")
```

## Request Details

**Background:** If it's a data request, grab from "What question(s) are you trying to answer?" and "Purpose of the request"

**Audience:** If it's a data request, grab from "Who is the intended audience?"

**Requester:** Requester name

**Date of Request:** Jan 1, 20xx

**Request Period:** AY20xx-20xx (xx years)

**Request Details:** (Record data from detail section of request in list format)

#### Data Sources

List all tables used.
